---
title: "GRANT 2026: SW QA/QC Tables"
output:
  html_document: default
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = F, eval=T)
library(dplyr)
library(kableExtra)
QAQC_tabs <- readRDS("QAQC_tabs.rds")
unfilt_tab_ls <- readRDS("unfilt_tab_ls.rds")
CT_tab_ls <- readRDS("CT_tab_ls.rds")
QAQC_tab_3 <- readRDS("QAQC_tab_3.rds")
QAQC_tab_raw_3 <- readRDS("QAQC_tab_raw_3.rds")
# saveRDS(DH_tag_code_summ,"QAQC_tab_raw_3.rds")

```
------------------------------------------------------------------------

# Unfiltered summary tables

## Status summary

### Live/Dead Status vs. survival_use

```{r usable_CT_tab,echo=F,eval=T,warning=FALSE}


kbl(unfilt_tab_ls$usable_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Live/Dead Status vs. Tagger

```{r fish_status_tagger_CT_tab,echo=F,eval=T,warning=FALSE}

# unfilt_tab_ls$fish_status_tagger_CT_tab

kbl(unfilt_tab_ls$fish_status_tagger_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Tarmac Fish

Fish that were dropped on the tarmac and should be excluded

```{r tarmac_tags,echo=F,eval=T,warning=FALSE}

# install.packages("kableExtra")
tarmac_tag_evt_tab <- readRDS("tarmac_tag_evt_tab.rds")
# saveRDS(tarmac_subb_tab,"tarmac_tag_evt_tab.rds")
# QAQC_tab_3 |> left_join(QAQC_tab2 |> select(repID,spp,RI_rel))
# left_join(QAQC_tab_3 |> select(repID,spp)) |> left_join(QAQC_tab2 |> select(repID,spp,RI_rel))

kbl(tarmac_tag_evt_tab )|> 
      # filter(spp=="STH" & fish_status!="Alive" & release_location=="Priest Rapids Tailrace") |>
      # select(-fish_status) |>
      # left_join(QAQC_tab2 |>
      #     select(repID,spp,PR_rel),by=c("spp", "repID")) |>
      # select(-Crescent.Bar,-Sunland,-Wanapum.BRZ,-Wanapum,-Wanapum.Tailrace,-Mattawa,-Priest.BRZ,-Priest) |>
      # relocate(spp,repID,PR_rel) 
                # )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")



```



------------------------------------------------------------------------

# Filtered summary tables

Focuses on 3284 fish in the `survival_use=TRUE` group. Fish in the `survival_use=FALSE` group are discussed in the final section. 

## Contingency Tables


### Release location vs. tagger

```{r RL_tagger_CT_tab,echo=F,eval=T,warning=FALSE}

# names(CT_tab_ls)
kbl(CT_tab_ls$RL_tagger_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Release location vs. helicopter

```{r RL_helicopter_CT_tab,echo=F,eval=T,warning=FALSE}

# names(CT_tab_ls)
kbl(CT_tab_ls$RL_helicopter_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Tag lot vs. Tagger

```{r lot_tagger_CT_tab,echo=F,eval=T,warning=FALSE}

# names(CT_tab_ls)
kbl(CT_tab_ls$lot_tagger_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Tag lot vs. Release location

```{r lot_RL_CT_tab,echo=F,eval=T,warning=FALSE}

# names(CT_tab_ls)
kbl(CT_tab_ls$lot_RL_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Replicate vs. Tagger

```{r repID_tagger_CT_tab,echo=F,eval=T,warning=FALSE}

# names(CT_tab_ls)
kbl(CT_tab_ls$repID_tagger_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Replicate vs. Release location

```{r repID_RL_CT_tab,echo=F,eval=T,warning=FALSE}

# names(CT_tab_ls)
kbl(CT_tab_ls$repID_RL_CT_tab) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

## Fish released by location, status, and tagger

### live fish

```{r QAQC_tab1a,echo=F,eval=T,warning=FALSE}

# install.packages("kableExtra")

QAQC_tab1 <- QAQC_tabs$"QAQC_tab1"

kbl(QAQC_tab1|> filter(tag_group=="live_release")) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

### Dead Fish

```{r QAQC_tab1b,echo=F,eval=T,warning=FALSE}
kbl(QAQC_tab1|> filter(tag_group=="dead_release")) |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

## Fish released by location, status, and replicate

### Chinook

```{r QAQC_tab2_CHN,echo=F,eval=T,warning=FALSE}

# install.packages("kableExtra")

QAQC_tab2 <- QAQC_tabs$"QAQC_tab2"

kbl(QAQC_tab2|> filter(spp=="CHN")) |>
    # kable_styling() |>
  kable_classic(full_width = F, html_font = "Times New Roman")

  
```

### Steelhead

```{r QAQC_tab2_STH,echo=F,eval=T}

kbl(QAQC_tab2|> filter(spp=="STH")) |>
    # kable_styling() |>
  kable_classic(full_width = F, html_font = "Times New Roman")

```

## `survival_use=FALSE` Fish detected by location and replicate

Includes fish-status categories: Euthanized, Mortality, and Tarmac

### Chinook

#### Rock Island

```{r QAQC_tab3_CHN_aRI,echo=F,eval=T,warning=FALSE}

kbl(QAQC_tab_3 |> 
      filter(spp=="CHN" & fish_status=="Alive" & release_location=="Rock Island Tailrace") |>
      select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,RI_rel),by=c("spp", "repID")) |>
      relocate(spp,repID,RI_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")


```

#### Priest Rapids

```{r QAQC_tab3_CHN_aPR,echo=F,eval=T,warning=FALSE}



kbl(QAQC_tab_3 |> 
      filter(spp=="CHN" & fish_status=="Alive" & release_location=="Priest Rapids Tailrace") |>
      select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,PR_rel),by=c("spp", "repID")) |>
      select(-Crescent.Bar,-Sunland,-Wanapum.BRZ,-Wanapum,-Wanapum.Tailrace,-Mattawa,-Priest.BRZ,-Priest) |>
      relocate(spp,repID,PR_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")



```

### Steelhead

#### Rock Island

```{r QAQC_tab3_STH_aRI,echo=F,eval=T,warning=FALSE}

kbl(QAQC_tab_3 |> 
      filter(spp=="STH" & fish_status=="Alive" & release_location=="Rock Island Tailrace") |>
      select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,RI_rel),by=c("spp", "repID")) |>
      relocate(spp,repID,RI_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")


```


#### Priest Rapids

```{r QAQC_tab3_STH_aPR,echo=F,eval=T,warning=FALSE}


kbl(QAQC_tab_3 |> 
      filter(spp=="STH" & fish_status=="Alive" & release_location=="Priest Rapids Tailrace") |>
      select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,PR_rel),by=c("spp", "repID")) |>
      select(-Crescent.Bar,-Sunland,-Wanapum.BRZ,-Wanapum,-Wanapum.Tailrace,-Mattawa,-Priest.BRZ,-Priest) |>
      relocate(spp,repID,PR_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")



```


## Fish in the `survival_use==FALSE` group detected site and replicate

### Chinook

#### Rock Island

```{r QAQC_tab3_CHN_dRI,echo=F,eval=T,warning=FALSE}

kbl(QAQC_tab_raw_3 |> 
      filter(spp=="CHN" & fish_status!="Alive" & release_location=="Rock Island Tailrace") |>
      # select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,RI_rel),by=c("spp", "repID")) |>
      relocate(spp,repID,RI_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")


```

#### Priest Rapids

```{r QAQC_tab3_CHN_dPR,echo=F,eval=T,warning=FALSE}


kbl(QAQC_tab_raw_3 |> 
      filter(spp=="CHN" & fish_status!="Alive" & release_location=="Priest Rapids Tailrace") |>
      # select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,PR_rel),by=c("spp", "repID")) |>
      select(-Crescent.Bar,-Sunland,-Wanapum.BRZ,-Wanapum,-Wanapum.Tailrace,-Mattawa,-Priest.BRZ,-Priest) |>
      relocate(spp,repID,PR_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")



```

### Steelhead

#### Rock Island

```{r QAQC_tab3_STH_dRI,echo=F,eval=T,warning=FALSE}


kbl(QAQC_tab_raw_3 |> 
      filter(spp=="STH" & fish_status!="Alive" & release_location=="Rock Island Tailrace") |>
      # select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,RI_rel),by=c("spp", "repID")) |>
      relocate(spp,repID,RI_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")


```

#### Priest Rapids

```{r QAQC_tab3_STH_dPR,echo=F,eval=T,warning=FALSE}


kbl(QAQC_tab_raw_3 |> 
      filter(spp=="STH" & fish_status!="Alive" & release_location=="Priest Rapids Tailrace") |>
      # select(-fish_status) |>
      left_join(QAQC_tab2 |>
          select(repID,spp,PR_rel),by=c("spp", "repID")) |>
      select(-Crescent.Bar,-Sunland,-Wanapum.BRZ,-Wanapum,-Wanapum.Tailrace,-Mattawa,-Priest.BRZ,-Priest) |>
      relocate(spp,repID,PR_rel) 
                )    |>
  kable_classic(full_width = F, html_font = "Times New Roman")



```






