---
title: "GRANT 2026; SW QA/QC Tables (1/2)"
format:
  docx:
    toc: true
    reference-doc: ref_doc.docx
editor: visual
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = F, eval=T)
library(dplyr)
options(knitr.kable.NA = '--')

CT_ALIVE_EUTH_ls <- readRDS("tmp_data/CT_ALIVE_EUTH_ls.rds")
CT_raw_ls <- readRDS("tmp_data/CT_raw_ls.rds")
rel_tagger_sum_tb_ls <- readRDS("tmp_data/rel_tagger_sum_tb_ls.rds")
rel_loc_by_repID_tabs <- readRDS("tmp_data/rel_loc_by_repID_tabs.rds")
```

{{< pagebreak >}}

# Summaries for all tags

Includes "Tarmac" and "Mortality" groups (i.e., fish dropped on the ground and that died during handing, respectively)

## Contingency Tables

### Live/Dead Status vs. survival_use

```{r ,echo=F,eval=T,warning=FALSE}

# summary of usability and status
knitr::kable(CT_raw_ls$"usable_CT_tab")
```

### Live/Dead Status vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$"fish_status_tagger_CT_tab")
```

### Release location vs. tagger

```{r ,echo=F,eval=T,warning=FALSE}

knitr::kable(CT_raw_ls$RL_tagger_CT_tab)

```

### Release Location vs. Release Type

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$RL_helicopter_CT_tab)
```

### Tag lot vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$lot_tagger_CT_tab)
```

### Tag lot vs. Release location

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$lot_RL_CT_tab)

```

### Tag lot vs. Tagger by Release location

#### Rock Island

##### CHN 

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$lot_tagger_RL_CT_tab_ls$"CHN.Rock Island Tailrace")
```

##### STH 

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$lot_tagger_RL_CT_tab_ls$"STH.Rock Island Tailrace")
```


#### Priest Rapids

##### CHN 

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$lot_tagger_RL_CT_tab_ls$"CHN.Priest Rapids Tailrace")
```

##### STH 

```{r ,echo=F,eval=T,warning=FALSE}

knitr::kable(CT_raw_ls$lot_tagger_RL_CT_tab_ls$"STH.Priest Rapids Tailrace")
```

### Replicate vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$repID_tagger_CT_tab)
```

### Replicate vs. Release location

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_raw_ls$repID_RL_CT_tab)
```

## Fish released by location, status, and tagger

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$all$tags_dat_raw_tagger_summ)
```

### Chinook

#### Live fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$all$tags_dat_raw_tagger_relID_summ_ls$CHN_live)
```

#### Dead fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$all$tags_dat_raw_tagger_relID_summ_ls$CHN_dead)
```

### Steelhead

#### Live fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$all$tags_dat_raw_tagger_relID_summ_ls$STH_live)
```

#### Dead fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$all$tags_dat_raw_tagger_relID_summ_ls$STH_dead)
```

------------------------------------------------------------------------

{{< pagebreak >}}

# Summaries based on `fish_status= "Alive" | fish_status= "Euthanized"`

Includes on 3284 live fish in the `survival_use=TRUE` group plus an additional 76 euthanized fish.

## Contingency Tables

### Live/Dead Status vs. survival_use

```{r usable_CT_tab,echo=F,eval=T,warning=FALSE}

# summary of usability and status
knitr::kable(CT_ALIVE_EUTH_ls$"usable_CT_tab")#$$usable_CT_tab)
```

### Live/Dead Status vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$"fish_status_tagger_CT_tab")
```

### Release location vs. tagger

```{r ,echo=F,eval=T,warning=FALSE}

knitr::kable(CT_ALIVE_EUTH_ls$RL_tagger_CT_tab)

```

### Release Location vs. Release Type

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$RL_helicopter_CT_tab)
```

### Tag lot vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$lot_tagger_CT_tab)
```

### Tag lot vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$lot_tagger_CT_tab)
```

### Tag lot vs. Release location

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$lot_RL_CT_tab)

```

### Replicate vs. Tagger

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$repID_tagger_CT_tab)
```

### Replicate vs. Release location

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(CT_ALIVE_EUTH_ls$repID_RL_CT_tab)
```

## Fish released by location, replicate, and Status

Rock Island and Priest Rapids are abbreviated and the "\_d" refers to release of "Euthanized" fish

### Chinook

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(rel_loc_by_repID_tabs$CHN)
```

### Steelhead

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(rel_loc_by_repID_tabs$STH)
```

## Fish released by location, status, and tagger

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$ALIVE_EUTH$tags_dat_ALIVE_EUTH_tagger_summ)
```

### Chinook

#### Live fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$ALIVE_EUTH$tags_dat_ALIVE_EUTH_tagger_relID_summ_ls$CHN_live)
```

#### Dead fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$ALIVE_EUTH$tags_dat_ALIVE_EUTH_tagger_relID_summ_ls$CHN_dead)
```

### Steelhead

#### Live fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$ALIVE_EUTH$tags_dat_ALIVE_EUTH_tagger_relID_summ_ls$STH_live)
```

#### Dead fish

```{r,echo=F}
knitr::kable(rel_tagger_sum_tb_ls$ALIVE_EUTH$tags_dat_ALIVE_EUTH_tagger_relID_summ_ls$STH_dead |> arrange(repID))
```