---
title: "GRANT 2026; SW QA/QC Tables (2/2)"
format:
  docx:
    toc: false
    reference-doc: ref_doc_w.docx
editor: visual
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = F, eval=T)
library(dplyr)

options(knitr.kable.NA = '--')

tag_DH_ls  <- readRDS("tmp_data/tag_DH_ls.rds")


```

# Detection Histories for All Tags

Includes "Tarmac" and "Mortality" groups (i.e., fish dropped on the ground and that died during handing, respectively)

## Live Fish

### Chinook

#### Rock Island Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_RI_summ" |> filter(spp=="CHN" & status=="Alive"))

```

#### Priest Rapids Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_PR_summ" |> filter(spp=="CHN" & status=="Alive"))

```

{{< pagebreak >}}

### Steelhead

#### Rock Island Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_RI_summ" |> filter(spp=="STH" & status=="Alive"))

```

#### Priest Rapids Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_PR_summ" |> filter(spp=="STH" & status=="Alive"))

```

{{< pagebreak >}}

## Dead Fish

### Chinook

#### Rock Island Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_RI_summ" |> filter(spp=="CHN" & status!="Alive"))

```

#### Priest Rapids Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_PR_summ" |> filter(spp=="CHN" & status!="Alive"))

```

{{< pagebreak >}}

### Steelhead

#### Rock Island Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_RI_summ" |> filter(spp=="STH" & status!="Alive"))

```

#### Priest Rapids Release

```{r ,echo=F,eval=T,warning=FALSE}
knitr::kable(tag_DH_ls$"raw_PR_summ" |> filter(spp=="STH" & status!="Alive"))

```
