---
title: "GRANT 2026; SW QA/QC Tables v3 (2/3)"
# title: "GRANT 2026; SW QA/QC Tables (2/2)"
format:
  docx:
    toc: true
    reference-doc: templates/docx/ref_doc_w.docx
editor: visual
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = F, eval=T)
library(dplyr)
library(tidyr)

options(knitr.kable.NA = '--')

# CT_ALIVE_EUTH_ls <- readRDS("tmp_data/CT_ALIVE_EUTH_ls.rds")
# CT_raw_ls <- readRDS("tmp_data/CT_raw_ls.rds")
# rel_tagger_sum_tb_ls <- readRDS("tmp_data/rel_tagger_sum_tb_ls.rds")
# rel_loc_by_repID_tabs <- readRDS("tmp_data/rel_loc_by_repID_tabs.rds")
# source("R/get_tagger_rel_loc_status_tb_ls.R")
# source("R/get_rel_loc_by_repID_tabs.R")
# source("R/get_conting_tabs.R")

tag_subsets_ls <- readRDS("tmp_data/tag_subsets_ls.rds")

# setwd("C:/repos/grant_2026/QAQC")
csv_fl_ls <- readRDS("tmp_data/csv_fl_ls.rds")
events_dat <- csv_fl_ls$GPUD2026_events_17Aug2026
node_dat <- csv_fl_ls$GPUD2026_nodes_12Aug2026

# tags_dat_ALIVE_EUTH_wrepID <- readRDS("tmp_data/tags_dat_ALIVE_EUTH_wrepID.rds")
# tags_dat_raw_wrepID <- readRDS("tmp_data/tags_dat_raw_wrepID.rds")

tag_subsets_ls <- readRDS("tmp_data/tag_subsets_ls.rds")

source("R/get_DH_tag_code_summ.R")


# tag_ALIVE_EUTH_DH_summ <- get_DH_tag_code_summ(node_dat_in = node_dat,events_dat_in = events_dat,tags_dat_wrepID_in = tags_dat_ALIVE_EUTH_wrepID)
# tag_raw_DH_summ <- get_DH_tag_code_summ(node_dat_in = node_dat,events_dat_in = events_dat,tags_dat_wrepID_in = tags_dat_raw_wrepID)


tag_ALIVE_EUTH_DH_summ <- get_DH_tag_code_summ(node_dat_in = node_dat,events_dat_in = events_dat,tags_dat_wrepID_in = tag_subsets_ls[["tags_ALIVE_or_EUTH"]])
tag_raw_DH_summ <- get_DH_tag_code_summ(node_dat_in = node_dat,events_dat_in = events_dat,tags_dat_wrepID_in = tag_subsets_ls[["RAW"]])


tag_raw_DH_summ <- tag_raw_DH_summ |> 
  rename(rel_loc=release_location,
         status=fish_status,CBAR=Crescent.Bar,WAN=Wanapum,WAN.BRZ=Wanapum.BRZ,WAN.TR=Wanapum.Tailrace,WB=White.Bluffs,HAN=Hanford,VRBR=Vernita.Bridge,PR.TR=Priest.Tailrace,PR.BRZ=Priest.BRZ,MATT=Mattawa,SUN=Sunland,LRNG=Lower.Ringold,PR=Priest) |>
  mutate(rel_loc=ifelse(rel_loc=="Rock Island Tailrace","RI","PR"))
tag_ALIVE_EUTH_DH_summ <- tag_ALIVE_EUTH_DH_summ |> 
  rename(rel_loc=release_location,status=fish_status,CBAR=Crescent.Bar,WAN=Wanapum,WAN.BRZ=Wanapum.BRZ,WB=White.Bluffs,HAN=Hanford,VRBR=Vernita.Bridge,PR.TR=Priest.Tailrace,PR.BRZ=Priest.BRZ,MATT=Mattawa,SUN=Sunland,LRNG=Lower.Ringold,PR=Priest) |>
  mutate(rel_loc=ifelse(rel_loc=="Rock Island Tailrace","RI","PR"))

names(tag_ALIVE_EUTH_DH_summ)

# AE_RI_summ <- tag_ALIVE_EUTH_DH_summ |> filter(rel_loc=="Rock Island Tailrace")
# AE_PR_summ <-  tag_ALIVE_EUTH_DH_summ |> filter(rel_loc=="Priest Rapids Tailrace")
# 
# raw_RI_summ <- tag_raw_DH_summ |> filter(rel_loc=="Rock Island Tailrace")
# raw_PR_summ <-  tag_raw_DH_summ |> filter(rel_loc=="Priest Rapids Tailrace")


AE_RI_summ <- tag_ALIVE_EUTH_DH_summ |> filter(rel_loc=="RI")
AE_PR_summ <-  tag_ALIVE_EUTH_DH_summ |> filter(rel_loc=="PR")

raw_RI_summ <- tag_raw_DH_summ |> filter(rel_loc=="RI")
raw_PR_summ <-  tag_raw_DH_summ |> filter(rel_loc=="PR")


tag_DH_ls <- list(
   "AE_RI_summ"=AE_RI_summ,
   "AE_PR_summ"=AE_PR_summ,
   "raw_RI_summ"=raw_RI_summ,
   "raw_PR_summ"=raw_PR_summ
   )

tag_DH_ls <- readRDS("tmp_data/tag_DH_ls.rds")

```

{{< pagebreak >}}

# Detection Histories for All Tags

## Live Fish


### Chinook

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_RI_summ' |> filter(spp=='CHN' & status=='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_PR_summ' |> filter(spp=='CHN' & status=='Alive'))
```
{{< pagebreak >}}

### Steelhead

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_RI_summ' |> filter(spp=='STH' & status=='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_PR_summ' |> filter(spp=='STH' & status=='Alive'))
```
{{< pagebreak >}}

## Dead Fish


### Chinook

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_RI_summ' |> filter(spp=='CHN' & status!='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_PR_summ' |> filter(spp=='CHN' & status!='Alive'))
```
{{< pagebreak >}}

### Steelhead

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_RI_summ' |> filter(spp=='STH' & status!='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'raw_PR_summ' |> filter(spp=='STH' & status!='Alive'))
```
{{< pagebreak >}}

# Detection Histories for `tags_SURVUSE_OR_EUTH_&_ACTIVE`

## Live Fish


### Chinook

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_RI_summ' |> filter(spp=='CHN' & status=='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_PR_summ' |> filter(spp=='CHN' & status=='Alive'))
```
{{< pagebreak >}}

### Steelhead

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_RI_summ' |> filter(spp=='STH' & status=='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_PR_summ' |> filter(spp=='STH' & status=='Alive'))
```
{{< pagebreak >}}

## Dead Fish


### Chinook

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_RI_summ' |> filter(spp=='CHN' & status!='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_PR_summ' |> filter(spp=='CHN' & status!='Alive'))
```
{{< pagebreak >}}

### Steelhead

#### Rock Island Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_RI_summ' |> filter(spp=='STH' & status!='Alive'))
```
#### Priest Rapids Release
```{r,echo=F,eval=T}
knitr::kable(tag_DH_ls$'SU_E_ACT_PR_summ' |> filter(spp=='STH' & status!='Alive'))
```
