---
title: "GRANT 2026; SW QA/QC Tables v3 (1/3)"
format:
  docx:
    toc: true
    reference-doc: ref_doc.docx
    execute:
warning: false
message: false  # Highly recommended to also hide package startup messages
editor: source
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = F, eval=T)
library(dplyr)
library(tidyr)

options(knitr.kable.NA = '--')

# CT_ALIVE_EUTH_ls <- readRDS("tmp_data/CT_ALIVE_EUTH_ls.rds")
# CT_raw_ls <- readRDS("tmp_data/CT_raw_ls.rds")
# rel_tagger_sum_tb_ls <- readRDS("tmp_data/rel_tagger_sum_tb_ls.rds")
# rel_loc_by_repID_tabs <- readRDS("tmp_data/rel_loc_by_repID_tabs.rds")
source("R/get_tagger_rel_loc_status_tb_ls.R")
source("R/get_rel_loc_by_repID_tabs.R")
source("R/get_conting_tabs.R")

tag_subsets_ls <- readRDS("tmp_data/tag_subsets_ls.rds")

```


{{< pagebreak >}}

# Summaries for all tags in the full data set (unfiltered)
Includes "Tarmac" and "Mortality" groups (i.e., fish dropped on the ground and that died during handing, respectively)

## Contingency Tables

### Live/Dead Status vs. Survival_use
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'usable_CT_tab'))
```
### Live/Dead Status vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'fish_status_tagger_CT_tab'))
```
### Release location vs. tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'RL_tagger_CT_tab'))
```
### Release Location vs. Release Type
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'RL_helicopter_CT_tab'))
```
### Tag lot vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'lot_tagger_CT_tab'))
```
### Tag lot vs. Release location
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'lot_RL_CT_tab'))
```

#### Rock Island

##### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'CHN.Rock Island Tailrace'))
```
##### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'STH.Rock Island Tailrace'))
```

#### Priest Rapids

##### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'CHN.Priest Rapids Tailrace'))
```
##### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'STH.Priest Rapids Tailrace'))
```
### Replicate vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'repID_tagger_CT_tab'))
```
### Replicate vs. Release location
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'repID_RL_CT_tab'))
```
## Fish released by location, status, and tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'tags_dat_raw_tagger_summ'))
```

### Chinook

#### Live fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'CHN_live'))
```
#### Dead fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'CHN_dead'))
```

### Steelhead

#### Live fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'STH_live'))
```
#### Dead fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'STH_dead'))
```

{{< pagebreak >}}


## Fish Released by Location, Replicate, and Status


Rock Island and Priest Rapids are abbreviated and the "_d" refers to release of "Euthanized" fish

#### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'rel_loc_by_repID_tabs',ele_nm_in = 'CHN'))
```
#### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['RAW']],tb_nm_in = 'rel_loc_by_repID_tabs',ele_nm_in = 'STH'))
```

{{< pagebreak >}}

# Summaries for all tags in the `tags_SURVUSE_OR_EUTH_&_ACTIVE` subset
Includes "Tarmac" and "Mortality" groups (i.e., fish dropped on the ground and that died during handing, respectively)

## Contingency Tables

### Live/Dead Status vs. Survival_use
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'usable_CT_tab'))
```
### Live/Dead Status vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'fish_status_tagger_CT_tab'))
```
### Release location vs. tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'RL_tagger_CT_tab'))
```
### Release Location vs. Release Type
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'RL_helicopter_CT_tab'))
```
### Tag lot vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'lot_tagger_CT_tab'))
```
### Tag lot vs. Release location
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'lot_RL_CT_tab'))
```

#### Rock Island

##### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'CHN.Rock Island Tailrace'))
```
##### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'STH.Rock Island Tailrace'))
```

#### Priest Rapids

##### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'CHN.Priest Rapids Tailrace'))
```
##### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'STH.Priest Rapids Tailrace'))
```
### Replicate vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'repID_tagger_CT_tab'))
```
### Replicate vs. Release location
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'repID_RL_CT_tab'))
```
## Fish released by location, status, and tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'tags_dat_raw_tagger_summ'))
```

### Chinook

#### Live fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'CHN_live'))
```
#### Dead fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'CHN_dead'))
```

### Steelhead

#### Live fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'STH_live'))
```
#### Dead fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'STH_dead'))
```

{{< pagebreak >}}


## Fish Released by Location, Replicate, and Status


Rock Island and Priest Rapids are abbreviated and the "_d" refers to release of "Euthanized" fish

#### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'rel_loc_by_repID_tabs',ele_nm_in = 'CHN'))
```
#### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_SURVUSE_OR_EUTH_&_ACTIVE']],tb_nm_in = 'rel_loc_by_repID_tabs',ele_nm_in = 'STH'))
```

{{< pagebreak >}}

# Summaries for all tags in the `tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER` subset
Includes "Tarmac" and "Mortality" groups (i.e., fish dropped on the ground and that died during handing, respectively)

## Contingency Tables

### Live/Dead Status vs. Survival_use
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'usable_CT_tab'))
```
### Live/Dead Status vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'fish_status_tagger_CT_tab'))
```
### Release location vs. tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'RL_tagger_CT_tab'))
```
### Release Location vs. Release Type
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'RL_helicopter_CT_tab'))
```
### Tag lot vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'lot_tagger_CT_tab'))
```
### Tag lot vs. Release location
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'lot_RL_CT_tab'))
```

#### Rock Island

##### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'CHN.Rock Island Tailrace'))
```
##### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'STH.Rock Island Tailrace'))
```

#### Priest Rapids

##### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'CHN.Priest Rapids Tailrace'))
```
##### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'lot_tagger_RL_CT_tab_ls',ele_nm_in = 'STH.Priest Rapids Tailrace'))
```
### Replicate vs. Tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'repID_tagger_CT_tab'))
```
### Replicate vs. Release location
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'repID_RL_CT_tab'))
```
## Fish released by location, status, and tagger
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'tags_dat_raw_tagger_summ'))
```

### Chinook

#### Live fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'CHN_live'))
```
#### Dead fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'CHN_dead'))
```

### Steelhead

#### Live fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'STH_live'))
```
#### Dead fish
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'tags_dat_raw_tagger_relID_summ_ls',ele_nm_in = 'STH_dead'))
```

{{< pagebreak >}}


## Fish Released by Location, Replicate, and Status


Rock Island and Priest Rapids are abbreviated and the "_d" refers to release of "Euthanized" fish

#### CHN
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'rel_loc_by_repID_tabs',ele_nm_in = 'CHN'))
```
#### STH
```{r,echo=F,eval=T}
knitr::kable(get_conting_tabs_by_name(tags_dat_in = tag_subsets_ls[['tags_ALIVE_ACTIVE_OTHER_OR_EUTH_ACTIVE_OTHER']],tb_nm_in = 'rel_loc_by_repID_tabs',ele_nm_in = 'STH'))
```
